Arc Blanc: a real time ocean simulation framework

### 2024-11-12 paper.tex
Fixed mask equations

Hence, \framework assumes that the interactive waves are solutions of the following classical 2-dimensional wave equation:
\begin{equation}
	\label{eq:2dwave}
	\nabla h(\mathbf x,t)-\frac{1}{c^2}\frac{\partial^2 h(\mathbf x,t)}{\partial t^2}=0
\end{equation}
where $h(\mathbf x,t)$ is the height of the water surface at horizontal position $\mathbf x$ and time $t$, $\nabla=\frac{\partial^2}{\partial x^2}+\frac{\partial^2}{\partial z^2}$ is the Laplacian in 2D and $c$ is the wave velocity expressed in $m.s^{-1}$.
\Framework uses the following Dirichlet boundary condition:
\begin{equation}
	h(\mathbf x,t) = 0 \text{~~~on the boundary.}
\end{equation}

@@

In the FDM simulation, \framework denotes by $h_{i,j}^n$ the water height $h(i\times dx,j\times dx,n \times dt)$ for discrete location $(i,j)\times dx$ and time $n\times dt$.
This leads to the following explicit scheme:
\begin{equation}
	\label{eq:fdm_scheme}
	h_{i,j}^{n+1} = a\left(h_{i+1,j}^n+h_{i-1,j}^n+h_{i,j+1}^n+h_{i,j-1}^n-4h_{i,j}^n\right) + 2h_{i,j}^n - h_{i,j}^{n-1}
\end{equation}
where
\begin{equation}
	a=\frac{c^2dt^2}{dx^2}.
\end{equation}
The Dirichlet boundary condition gives $h_{i,j}^n=0$ for $i$ or $j$ being on the boundary of $Z$.
Since a new wave is generated at each time step, a damping effect is added to make them disappear gradually.
Hence, the right part of Equation (\ref{eq:fdm_scheme}) is multiplied by the \textbf{damping factor} $d(t)=d^n$.
This damping factor is linearly related to the velocity of the mesh $v_M(t)$ to ensure numerical stability as follows:
\begin{equation}
	d(t) =
	\begin{cases}
		\left(1-\frac{||v_M(t)||}{v_{max}}\right)d_0 + \frac{||v_M(t)||}{v_{max}}d_{max} & \text{for~~}||v_M(t)||\leq v_{max}, \\
		d_{max}                                                                          & \text{else}
	\end{cases}
\end{equation}
where $d_{max}$ is the maximum damping value obtained when the body's velocity is above a given threshold $v_{max}$,
and $d_0$ is the damping for a null velocity.
For a plausible appearance, \framework uses the following values by default:
\begin{equation}
	\begin{cases}
		d_0     & = 0.98,       \\
		d_{max} & = 0.999,      \\
		v_{max} & = 5 m.s^{-1}.
	\end{cases}
\end{equation}
Nevertheless, the user can adjust these values in a way that a body $M$ causes more or less interaction waves.

@@

While $h_b$ is defined by the user, the value of $w_f$ is estimated as follows:
\begin{equation}
	h_f = V_{M}h_{M}\times i_f\times\frac{v_w}{v_{M}},
\end{equation}
where $V_M$ is the velocity of the body $M$, $h_M$ is the full height of $M$, $i_f$ is a user parameter allowing more user control, $v_w$ is the submerged volume of $M$ (\cf Section~\ref{sec:fluidToSolidAction}), and $v_{M}$ is the full volume of $M$.
Hence, for more realism $h_f$ is made proportional to the velocity of $M$:
the faster $M$ moves, the bigger the waves generated by $M$ at its front are.

>>>>

Hence, \framework assumes that the interactive waves are solutions of the following classical 2-dimensional wave equation:
\begin{equation}
	\label{eq:2dwave}
	\Delta h(\mathbf x,t)-\frac{1}{c^2}\frac{\partial^2 h(\mathbf x,t)}{\partial t^2}=0
\end{equation}
where $h(\mathbf x,t)$ is the height of the water surface at horizontal position $\mathbf x$ and time $t$, $\Delta=\frac{\partial^2}{\partial x^2}+\frac{\partial^2}{\partial z^2}$ is the Laplacian in 2D and $c$ is the wave velocity expressed in $m.s^{-1}$.
\Framework uses the following Dirichlet boundary condition:
\begin{equation}
	h(\mathbf x,t) = 0 \text{~~~on the boundary.}
\end{equation}

@@

In the FDM simulation, \framework denotes by $h_{i,j}^n$ the water height $h(i\times dx,j\times dx,n \times dt)$ for discrete location $(i,j)\times dx$ and time $n\times dt$.
This leads to the following explicit scheme:
\begin{equation}
	\label{eq:fdm_scheme}
	h_{i,j}^{n+1} = a\left(h_{i+1,j}^n+h_{i-1,j}^n+h_{i,j+1}^n+h_{i,j-1}^n-4h_{i,j}^n\right) + 2h_{i,j}^n - h_{i,j}^{n-1}
\end{equation}
where
\begin{equation}
	a=\frac{c^2dt^2}{dx^2}.
\end{equation}
The Dirichlet boundary condition gives $h_{i,j}^n=0$ for $i$ or $j$ being on the boundary of $Z$.
Since a new wave is generated at each time step, a damping effect is added to make them disappear gradually.
Hence, the right part of Equation (\ref{eq:fdm_scheme}) is multiplied by the \textbf{damping factor} $d(t)=d^n$.
This damping factor is linearly related to the velocity of the mesh $v_M(t)$ to ensure numerical stability as follows:
\begin{equation}
	d(t) =
	\begin{cases}
		\left(1-\frac{||\mathbf{v_M}(t)||}{v_{max}}\right)d_0 + \frac{||v_M(t)||}{v_{max}}d_{max} & \text{for~~}||v_M(t)||\leq v_{max}, \\
		d_{max}                                                                          & \text{else}
	\end{cases}
\end{equation}
where $d_{max}$ is the maximum damping value obtained when the body's velocity is above a given threshold $v_{max}$,
and $d_0$ is the damping for a null velocity.
For a plausible appearance, \framework uses the following values by default:
\begin{equation}
	\begin{cases}
		d_0     & = 0.98,       \\
		d_{max} & = 0.999,      \\
		v_{max} & = 5 m.s^{-1}.
	\end{cases}
\end{equation}
Nevertheless, the user can adjust these values in a way that a body $M$ causes more or less interaction waves.

@@

While $h_b$ is defined by the user, the value of $w_f$ is estimated as follows:
\begin{equation}
	h_f = \mathbf{v_M}h_{M}\times i_f\times\frac{v_w}{v_{M}},
\end{equation}
where $\mathbf{v_M}$ is the velocity of the body $M$, $h_M$ is the full height of $M$, $i_f$ is a user parameter allowing more user control, $v_w$ is the submerged volume of $M$ (\cf Section~\ref{sec:fluidToSolidAction}), and $v_{M}$ is the full volume of $M$.
Hence, for more realism $h_f$ is made proportional to the velocity of $M$:
the faster $M$ moves, the bigger the waves generated by $M$ at its front are.
